abc

### 2024-09-23 randpython.qmd
autorun

    allrot = [ps[i] for i in sel]
    return allrot

def genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g'):
    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
    x, y, z = sympy.symbols('x y z')
    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
    parm = elem[2-1][:5]
    ls, rs = expr.split('=')
    expr = Eq(sympify(ls), sympify(rs))
    plr = int(sympy.total_degree(expr))-1
    polys = poly(expr.rhs - expr.lhs, sympify(solv)).all_coeffs()
    abc = [1,0,0,0,1,0,0,0,1]
    uvw = []
    ABCDE = [0, 0, 0, 0, 0]
    ABCDE[:len(polys)] = polys
    matarch = 0
    return ABCDE, abc, matarch, plr

#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')

def genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4]):
    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]

@@

    parm = elem[form-1][:5]

@@

        D[0] += dic['d_300']*y**3 + dic['d_301']*y*z**2 + dic['d_302']*y**2*y+dic['d_303']*z**3
        D[1] += dic['d_300']*x**3 + dic['d_310']*x*y**2 + dic['d_320']*y**2*x+dic['d_330']*y**3

@@

        D[0] += dic['d_100']*z + dic['d_101']*y+dic['d_000']
        D[1] += dic['d_100']*z + dic['d_110']*x+dic['d_000']
        D[2] += dic['d_101']*y + dic['d_110']*x+dic['d_000']

@@

```{pyodide-python}
#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='alpha',eur=[1, 2, 4])
#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='x',eur=[1, 2, 4])[0]
#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4])[0]
#genpolycoeffr(form=2,expr="z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",solv='alpha',eur=[1, 2, 4])
```

```{pyodide-python}
def pareq(ste='(x + y*zeta)/(zeta + 1)', **kwargs):
    return eval(ste, kwargs)
```

```{pyodide-python}
pareq(ste='(x + y*zeta)/(zeta + 1)', x=0.75, y=0.25, zeta=1)
pareq(ste='(x + y*zeta)/(zeta + 1)', y=0.25, zeta=1,x=2.75)
```

>>>>

    allrot = [ps[i] for i in sel]
    return allrot
```

```{pyodide-python}
def genpolycoeffn(form,expr,solv):
    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
    x, y, z = sympy.symbols('x y z')
    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
    parm = elem[2-1][:5]
    ls, rs = expr.split('=')
    expr = Eq(sympify(ls), sympify(rs))
    plr = int(sympy.total_degree(expr))-1
    polys = poly(expr.rhs - expr.lhs, sympify(solv)).all_coeffs()
    abc = [1,0,0,0,1,0,0,0,1]
    uvw = []
    ABCDE = [0, 0, 0, 0, 0]
    ABCDE[:len(polys)] = polys
    matarch = 0
    return ABCDE, abc, matarch, plr

```{pyodide-python}
def genpolycoeffr(elem,expr,solv,eur):
    #elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]

@@

    parm = elem #elem[form-1][:5]

@@

        D[0] += dic['d_300']*y**3 + dic['d_301']*y*z**2 + dic['d_302']*y**2*y + dic['d_303']*z**3
        D[1] += dic['d_300']*x**3 + dic['d_310']*x*y**2 + dic['d_320']*y**2*x + dic['d_330']*y**3

@@

        D[0] += dic['d_100']*z + dic['d_101']*y + dic['d_000']
        D[1] += dic['d_100']*z + dic['d_110']*x + dic['d_000']
        D[2] += dic['d_101']*y + dic['d_110']*x + dic['d_000']

@@

```{pyodide-python}
testn = genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
```

```{pyodide-python}
testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha')
```

```{r, echo=F, eval=T}
knitr::knit_exit()
```
